Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-06 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: clarify SVM filter vs no filter performance

% filters
% - influence varies based on algorithm and task (SVM no influence, RF medium, XGB medium)
% - no substantial decrease in performance when using filters
% - no advantage of ensemble borda filter compared to others
Effects of filter methods on performance differed greatly between algorithms:
SVM showed no variation in performance across filters (\autoref{fig:filter-effects-no-filter}).
Using filters for RF showed a substantial increase in performance for all tasks with the exception of VI, for which the difference among all filters was also the smallest (\autoref{fig:filter-effects-no-filter}).
XGBoost showed a high dependency on filtering the data: In 4 out of 6 tasks using no filter would results in the worst or second worst performance.
However, in contrast for dataset NRI using no filter results in the best performance.
XGBoost shows the highest overall differences between filters for a single task: For dataset HR, the range is up to 14 percentage points (Carscore vs. no filter)(\autoref{fig:filter-effects-no-filter}).

% filter vs. no filter
% - Substantial effect for XGBoost and RF
% - SVM unaffected
When comparing the usage of filters against using no filter at all, there was only one instance (XGBoost on the NRI task) when the model without filtering showed a slighly better performance than the best filtered one (\autoref{fig:filter-effects-no-filter}).
For SVM filters and no filter come in at the same performance for tasks VI and NRI even though \autoref{fig:filter-effects-no-filter} lists "No Filter" as the best option.

>>>>

% filters
% - influence varies based on algorithm and task (SVM no influence, RF medium, XGB medium)
% - no substantial decrease in performance when using filters
% - no advantage of ensemble borda filter compared to others
Effects of filter methods on performance differed greatly between algorithms:
SVM showed no variation in performance across filters (\autoref{fig:filter-effects-no-filter}).
Using filters for RF showed a substantial increase in performance for all tasks with the exception of VI, for which the difference among all filters was also the smallest (\autoref{fig:filter-effects-no-filter}).
XGBoost showed a high dependency on filtering the data: In 4 out of 6 tasks using no filter would results in the worst or second worst performance.
However, in contrast for dataset NRI using no filter results in the best performance.
XGBoost shows the highest overall differences between filters for a single task:
For feature set HR, the range is up to 14 percentage points (Carscore vs. no filter)(\autoref{fig:filter-effects-no-filter}).

% filter vs. no filter
% - Substantial effect for XGBoost and RF
% - SVM unaffected
When comparing the usage of filters against using no filter at all, there was only one instance (XGBoost on the NRI task) when the model without filtering showed a slighly better performance than the best filtered one (\autoref{fig:filter-effects-no-filter}).
For SVM, all filters and 'no filter' achieved the same performance on tasks VI and NRI even though \autoref{fig:fig:perf-result} lists "No Filter" as the best option.
